---
title: "TidyCoral"
author: "Subin / Connor"
date: "2024-02-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor) # install.packages('janitor')
library(skimr) # install.packages('skimr')
library(stringr)# added when we needed it for benthic data
library(dplyr)
library(plotly) #makes ggplot interactive
```

```{r}
benthic_url <- 'https://www.nodc.noaa.gov/archive/arc0054/0104255/1.1/data/0-data/cd08/100308OaAla03m.CSV'

## buoy data
buoy_url <- 'http://www.ndbc.noaa.gov/view_text_file.php?filename=mokh1h2010.txt.gz&dir=data/historical/stdmet/'
```

```{r}
benthic_raw <- read_csv(benthic_url)
head(benthic_raw) 
```

using janitor package to clean column headers 
line 31 good for cleaning messy column headers 
```{r}
benthic <- benthic_raw %>%
  janitor::clean_names()
names (benthic)
```
```{r}
benthic <- benthic %>% 
  select(id_name, point, x,y, id_date)
head(benthic)
```
remove the leading and trailing hastags 
create a column called date
```{r}
benthic <- benthic %>%
  mutate(date = stringr::str_remove_all(id_date, "#"))
```

look at summary stats
line 51 shows us unique dates and species 
```{r}
summary(benthic)
skimr::skim(benthic)
```

check which species are represented 
```{r}
unique(benthic$id_name)
```
species count by date 
```{r}
benthic_coverage_plot <- ggplot(benthic,aes(date,fill=id_name))+
  geom_bar()+
theme_light()+
labs(title = "Benthic Coverage",
     subtitle = "NCEAS Tidy Coral",
     X = "Date",
     y = "Number of Individuals",
     fill = "benthic ID")+
  scale_fill_viridis_d()

benthic_coverage_plot
```
^^ "why do  the total counts increase rapidly overtime?" 

Plot 
```{r}
ggplotly(benthic_coverage_plot)
```

Buoy Data 

import from url 
```{r}
buoy <- readr::read_csv(buoy_url)
head(buoy)
```
not working and also local import file due to fixed width file so use read_table2()
```{r}
buoy_raw <- read_table2(buoy_url, skip = 1)
head(buoy_raw)
```


```{r}

buoy_test <- read_lines(buoy_url)
y <- buoy_test %>%
  as_data_frame() %>%
  mutate(value = str_replace_all(value, ' +', ',')) 
write_delim(y, 'data/buoy_local_copy.csv')

z <- read_csv('data/buoy_local_copy.csv', )
head(z)
```

95 is a function to create the directory 

```{r}
dir.create("data")
write_delim(y, 'C:/Users/chosu/OneDrive/Documents/Data-4-SDG/TidyCoral/data/buoy_local_copy.csv')

```

```{r}
buoy_test <- read_lines(buoy_url)
y <- buoy_test %>%
  as_data_frame() %>%
  mutate(value = str_replace_all(value, ' +', ',')) 
tryCatch({
  write_delim(y, 'data/buoy_local_copy.csv')
}, error = function(e) {
  print(paste("Error:", e$message))
})

z <- read_csv('data/buoy_local_copy.csv', skip=1)
head(z)
```

```{r}
buoy <- buoy_raw
names(buoy)
head(buoy)
```




